\Huge \bf \sc Calibration of an inertial measurement unit

### 2013-07-29 latex/paper_sensores/paper.tex
sasdf
asdf

\section{Introduction}
The development of the Micro-electromechanical Systems (MEMS) technology has allowed to manufacture many low-cost chip-sensors, such as accelerometers, gyroscopes and magnetometers. Those chips have been adopted in many applications, for instance Inertial Navigation Systems (INS), \cite{bib:paper}. However this sensors have many error sources, thus, they must be calibrated before being used and they should be re-calibrated periodically for any precision application. The different sources of error will be analyzed in more detail in Section \refp{sec:modelo} and the implications of those errors will be derived.\\

@@

>>>>

\section{Introduction}
The development of the Micro-electromechanical Systems (MEMS) technology has allowed to manufacture many low-cost chip-sensors, such as accelerometers, gyroscopes and magnetometers. Those chips have been adopted in many applications, for instance Inertial Navigation Systems  (INS)\cite{bib:un_puto_nuevo}. However this sensors have many error sources, thus they must be calibrated before being used and they should be re-calibrated periodically for any precision application. The different sources of error will be analysed in more detail in section \refp{sec:modelo} and the implications of those errors will be derived.\\

The calibration proposed in this paper is tested on a 3-axis accelerometer ADXL345 of Analog Devices and a 3-axis gyroscope ITG-3200  of InvenSense, yet the model developed and the methodology can be used in other devices because the model is based on common characteristics of MEMS sensors. The sensors named before are included in a Inertial Measurement Unit(IMU): The Mongoose (figure \refp{fig:mongoose}). \\

@@

\begin{figure}
	\centering
	\includegraphics[width=.6\columnwidth]{./pics_paper/mesa_esquema.png}
	\caption{\textbf{Adjustable table}- Scheme}
	\label{fig:mesa_esquema}
\end{figure}
